Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2016-06-06 Paper/Manuscript.tex
Petit changement

There is no justification for this aggregation method. We argue that
all the results they reach that are not a reformulation of the
evolution of the openness ratio during the two
globalizations come from this aggregation technique.\\

>>>>

There is no justification for this aggregation method. We argue that
all the results they reach that are not a reformulation of the
evolution of the openness ratio during the two
globalizations come from this aggregation method.\\
